\documentclass{resume}

\usepackage{multicol}
\usepackage[left=0.7in,top=0.4in,right=0.5in,bottom=0.5in]{geometry}

\usepackage[inline]{enumitem}
\name{Eli Kirmayer}
\address{ 72 Corte Yolanda \\ Moraga, CA 94556  }
\address{ 925~$\cdot$~408~$\cdot$~7663 \\ kirmayer.e@husky.neu.edu }
\def\nameskip{\smallskip}
\def\sectionskip{\smallbreak}

\begin{document}
%\begin{center}
%Third year Computer Science student eager to gain experience in the software industry.  Prior experience with python, relational and %NoSQL databases, web frameworks, and machine learning.  Interested in all things data and web related.
%\end{center}


  \begin{rSection}{Technical Strengths}
    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
      Computer Languages & Python, Java, C, R, SQL, HTML/CSS/JavaScript, PERL, AMD64 Assembly \\
      Databases & MySQL, Elasticsearch, Redis, MongoDB, SQLite, PostgreSQL \\
      Tools \& Operating Systems & Git, Perforce, \LaTeX, SolidWorks, Tableau, macOS, Windows, Linux \\
    \end{tabular}
  \end{rSection}
  
  
  
    \begin{rSection}{Education}
    {\bf Northeastern University - B.S. in Computer Science} \hfill {\em 2016 - Present (2021 expected)} \\ 
    \textbf{Honors: }GPA: 3.85, Dean's List 2016 onward \\
     \textbf{Course Assistant:} Principles of Information Science; Data Collection, Integration, and Analysis; Database Design; Large-Scale Information Storage \& Retrieval
    
  \end{rSection}
  
  \begin{rSection}{Experience}
  
        \begin{rSubsection}{NVIDIA}{October 2018 - December 2018, May 2019 - December 2019}{Software Engineering Co-op, MTS Tools Team}{Santa Clara, CA}
    \item Worked on an internal Django dashboard designed to display CPU microcode performance.
    \item Upgraded CPU build dashboard to a more recent Python version and library releases.
    \item Migrated CPU tracer explorer with same Python version and library releases.
    \item Displayed relevant CPU performance comparisons between runs for smoother workflow.
    \item Designed Django and Selenium testing suites to accompany and assist tool upgrade processes.
    \item Fixed CPU build code for MISRA Safety compliance.
 %\end{rSubsection}
 
  %    \begin{rSubsection}{NVIDIA}{October 2018 - December 2018}{Software Engineering Co-op, MTS Tools Team}{Santa Clara, CA}
    \item Provided feedback on comprehensibility of code written and maintained by a single person.
    \item Redesigned table data extraction and formatting to better present information organized by date.
    \item Implemented frontend and cURL HTTP file upload.
    \item Extracted and integrated source control information regarding performance tests results into front-end displays.
 \end{rSubsection}
 
    \begin{rSubsection}{NVIDIA}{May 2018 - October 2018}{Software Engineering Co-op, Silicon Solutions Group}{Santa Clara, CA}
    \item Designed a web interface to interact with existing GPU data, eliminated man-hour bottlenecks automating Perl-module creation for new projects, and created a user interface to simplify modification of existing files.
    \item Worked closely with a team of electrical engineers to meet requirements for tools to assist their work.
    \item Created a Python library that parses Perl source and loads literals as Python dictionaries.
    \item Refactored Perl scripts to a Python server API to simplify clock-speed calculations.
    \end{rSubsection}

    %\begin{rSubsection}{Northeastern University}{September 2017 - April 2018}{Course Assistant - Principles of Information %Science \& 	    Data Collection, Integration, and Analysis}{Boston, MA}
    %\item Graded assignments and helped students understand machine learning, data collection, and database topics. 
    %\item Held office hours twice a week for students to get help, work on assignments, and understand lecture material.
    %\end{rSubsection}
  
    \begin{rSubsection}{Findera}{May 2017 - August 2017}{Software Engineering Intern}{San Francisco, CA}
    \item Led design and creation of a Naive Bayes classifier to identify job titles based on Linkedin resum\'es.
    \item Handled frontend website feature requests and bug fixes in Javascript.
    \item Automated HTML data extraction along the data pipeline using Spark and XQuery.
    \item Built an internal dashboard to create data-transformation rules using Flask and Elasticsearch.
    \end{rSubsection}

    \begin{rSubsection}{Pyze, Inc}{June 2016 - August 2016}{Software Engineering Intern}{Redwood City, CA}
    \item Designed Python scripts to populate demo accounts with human-like app usage data.
    \item Implemented automated email scripts for new customers to receive welcome emails on signup.
    \end{rSubsection}

  \end{rSection}

  \begin{rSection}{Projects}
  
      \begin{rSubsection}{Delivery Tracking API}{August 2019 - Present}{}{}
    \item Created a RESTful API to store and track packages in a single location via tracking numbers.
    \item Built a custom user login system, package store, and scraping system using MongoDB and BeautifulSoup.
  \end{rSubsection}
  
    \begin{rSubsection}{Counter Strike: Global Offensive Data Visualizer}{February 2019}{}{}
    \item Extracted live gamestate data into a visualization tool to track user progress and statistics.
  \end{rSubsection}
  
  \begin{rSubsection}{Real-time Trading Marketplace}{March 2018 - April 2018}{}{}
      \item Implemented a real-time trading market in Redis to place buy and sell orders for in-game items.
  \end{rSubsection}

  \end{rSection}
  

  
%    \begin{rSection}{Hobbies \& Interests}
%  $\bullet$ Cars \hfill $\bullet$ Mechanical Keyboards \hfill $\bullet$ Video Games \hfill $\bullet$ Cooking \hfill $\bullet$ Percussion
 %\end{rSection}
  

\end{document}